A meta-analysis of mental rotation ability in the first years of life

### 2022-04-13 code/analysis.Rmd
Add notes for performing split/mixed analyses

```{r, simulation}
generate_exp <- function(id,
                         n_boys = 1e3,
                         n_girls = 1e3,
                         mean_diff_boys = 0,
                         mean_diff_girls = 2,
                         sd_diff_boys = 4,
                         sd_diff_girls = 4) {

@@

  # Return all results for this experiment as a list
  return(list(
    id = id,
    n_boys = n_boys,
    n_girls = n_girls,
    n_infants = n_infants,
    d_boys = d_boys,
    d_girls = d_girls,
    d_infants = d_infants
  ))
}

# Generate random experiments
n_boys <- 1e3
n_girls <- 1e3
n_exps <- 100
ids <- paste0("exp_", 1:n_exps)
dat <- lapply(ids, generate_exp, n_boys, n_girls)
dat <- do.call(rbind.data.frame, dat)

@@

# Fit 3 level meta-analysis
res_full <- metafor::rma.mv(
  d_infants, v_d_infants,
  random = ~ id | id,
  data = dat,
  slab = id
)

# Check results
summary(res_full)
```

>>>>

```{r, simulation}
generate_exp <- function(n_boys = 1e3,
                         n_girls = 1e3,
                         mean_diff_boys = 0,
                         mean_diff_girls = 2,
                         sd_diff_boys = 4,
                         sd_diff_girls = 4) {

@@

  # Return all results for this experiment as a list
  return(list(
    n_boys = n_boys,
    n_girls = n_girls,
    n_infants = n_infants,
    d_boys = d_boys,
    d_girls = d_girls,
    d_infants = d_infants
  ))
}

# Generate random experiments
n_boys <- 1e3
n_girls <- 1e3
n_exps <- 100
dat <- replicate(n_exps, generate_exp(n_boys, n_girls), simplify = FALSE)
dat <- do.call(rbind.data.frame, dat)
dat$id <- paste0("exp_", 1:n_exps)

@@

# Fit 3 level meta-analysis
res_full <- metafor::rma.mv(
  d_infants, v_d_infants,
  # random = ~ id | id,
  data = dat,
  slab = id
)

# Check results
summary(res_full)

### SPLIT EXPERIMENTS ONLY ###

# Put effect sizes for boys and girls into separate rows
dat_split <- tidyr::pivot_longer(
  dat,
  cols = c(d_boys, d_girls),
  names_to = "gender",
  values_to = "d_gender"
)

# Compute sampling variance of the gender-specific effect size
dat_split$v_d_gender <- with(
  dat_split, ((2 * (1 - r_assumed)) / n_girls) + (d_gender^2 / (2 * n_girls))
)

# Use rma.mv to compute MA on d_gender and v_d_gender values

# Repeat 100 times with generate_meta

# Compare mixed gender and split gender MAs
# Same distribution of meta-analytic effect size?
# Same variance / standard error?
# Is the difference significant?

### MIXED/SPLIT GENDER ANALYSIS ###

# Make a percentage of study use mixed vs. split and choose randomly
# Use different percentages
# Make split vs. mixed dependent on the observed gender difference
# Note for this we need to draw study specific effect sizes from a distribution

### MAKE IT MORE REALISTIC ###

# Make sample sizes per study different

# Automate
generate_meta <- function(n_exps, n_boys, n_girls) {

  # Generate random experiments
  dat <- replicate(n_exps, generate_exp(n_boys, n_girls), simplify = FALSE)
  dat <- do.call(rbind.data.frame, dat)
  dat$id <- paste0("exp_", 1:n_exps)

  # Fit meta-analysis
  res_full <- metafor::rma.mv(
    d_infants, v_d_infants,
    # random = ~ id | id,
    data = dat,
    slab = id
  )

  # Return coefficients table
  summ <- summary(res_full)
  return(coef(summ))
}

n_metas <- 100
metas <- replicate(n_metas, generate_meta(100, 100, 100), simplify = FALSE)
metas <- do.call(rbind.data.frame, metas)
metas$id <- paste0("meta_", 1:n_metas)

mean(metas$estimate)
```
